---
title: "LME_pfac_PRS"
author: "Kevin Sun"
date: "3/14/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width=250)
library(tidyr)
library(dplyr)
library(ggplot2)
library(lsr)
library(lme4)
library(lmerTest)
library(mediation)
library(ggcorrplot)
library(corrplot)
library(RColorBrewer)
library(glmnet)
library(mgcv)
library(gamm4)
library(readr)

library(devtools)
#install_github("jfortin1/neuroCombatData")
#install_github("jfortin1/neuroCombat_Rpackage")
library(neuroCombat)

library(R.matlab)
library(mgcv)
library(ggplot2)
library(visreg)
library(ggtext)
library(sjPlot)
library(Gmisc)

library(lmtest)
library(optimx)
library(lmeresampler)
```

## Import the bifactor scores, covariates from DEAP
```{r}
newdata<-readRDS("DEAP-data-download_ABCD_psychopathology_bifactor_scores_BASELINE.rds")
newdata.baseline<-newdata[newdata$event_name=="baseline_year_1_arm_1",]
colnames(newdata.baseline)[1]<-"subjectkey"
all.data <- newdata.baseline #11,876
```


# Add in Family, Age, and Site covariates
```{r}
family <-read.table("../acspsw03.txt",header=TRUE)
family.baseline<-family[family$eventname=="baseline_year_1_arm_1",]
abcd.data.almost <- merge(all.data,family.baseline[, c("subjectkey", setdiff(colnames(family.baseline),colnames(all.data)))],by="subjectkey")
site_info <- readRDS("../DEAP-siteID.rds")
site.baseline<-site_info[site_info$event_name=="baseline_year_1_arm_1",]
colnames(site.baseline)[1]<-"subjectkey"
abcd.data <- merge(abcd.data.almost,site.baseline[,c("subjectkey", setdiff(colnames(site.baseline),colnames(abcd.data.almost)))],by="subjectkey") #11,875
```


# Load discovery/replication matched samples -- Changed: matched_group 1 & 2 (>0) -> combined group
```{r}
traintest<-read_tsv("../participants.tsv")
traintest.baseline<-traintest[traintest$session_id=="ses-baselineYear1Arm1",c("participant_id","matched_group")]
colnames(traintest.baseline)[1]<-c("subjectkey")
traintest.baseline$subjectkey <- gsub(pattern="sub-NDAR",replacement="NDAR_", traintest.baseline$subjectkey)
traintest.baseline<-traintest.baseline %>% distinct()
abcd.data.traintest <- merge(abcd.data,traintest.baseline,by="subjectkey")
abcd.data.traintest<-abcd.data.traintest[!duplicated(abcd.data.traintest$subjectkey),] # remove duplicated subject
abcd.data.combined <- abcd.data.traintest[abcd.data.traintest$matched_group>0,] #11,873
```

# Apply ComBat harmonization across ABCD sites separately for combined set
```{r}
# prep to make sure there are no empty levels
abcd.data.combined$abcd_site<-droplevels(abcd.data.combined$abcd_site)

# harmonize combined set 
batch <- abcd.data.combined$abcd_site
abcd.data.combined.toharmonize <- abcd.data.combined[,c("Factor4")]
mod <- model.matrix(~abcd.data.combined$interview_age+abcd.data.combined$sex+abcd.data.combined$rel_family_id)
dat <- t(abcd.data.combined.toharmonize)
abcd.data.combat <- neuroCombat(dat=dat,mod=mod,batch=batch,eb=FALSE)
dat.harmonized<-data.frame(t(abcd.data.combat$dat.combat))
abcd.data.nopfac <- subset(abcd.data.combined,select=-c(Factor4))
abcd.data.combined.harmonized <- cbind(abcd.data.nopfac,dat.harmonized) # Add the harmonized data back into the main dataframe (BE AWARE THAT NOT ALL DATA IS HARMONIZED)
colnames(abcd.data.combined.harmonized)[58]<-"Factor4"

```


# fix age variable to be continuous
```{r}
abcd.data.combined.harmonized$interview_age <- as.numeric(abcd.data.combined.harmonized$interview_age)
abcd.data.traintest$interview_age <- as.numeric(abcd.data.traintest$interview_age) #5815
```


# standardize age, meanFD, and PFN size
```{r}
abcd.data.combined.harmonized$interview_age<-(abcd.data.combined.harmonized$interview_age-mean(abcd.data.combined.harmonized$interview_age,na.rm=TRUE))/sd(abcd.data.combined.harmonized$interview_age,na.rm=TRUE)

```

# Import PRS scores
```{r}
#for simplicity, rename PRS column titles
PRS1 <- read.csv('../Residual_ABCD_EUR_Mallard_Factor_1_PRS.csv')
PRS2 <- read.csv('../Residual_ABCD_EUR_Mallard_Factor_2_PRS.csv')

colnames(PRS1)[2]<-c("subjectkey") #make subject col name consistent
colnames(PRS2)[2]<-c("subjectkey")
colnames(PRS1)<-gsub("Residual_PRS_1","PRS_1",colnames(PRS1)) #simplify PRS col names
colnames(PRS2)<-gsub("Residual_PRS_2","PRS_2",colnames(PRS2))

PRS1$subjectkey<-gsub('INV','NDAR_INV',PRS1$subjectkey) #match subject id format
PRS2$subjectkey<-gsub('INV','NDAR_INV',PRS2$subjectkey)

PRS1_alone <- PRS1[, c('subjectkey','PRS_1')] #subset dataframes with only subjectkey and PRS columns
PRS2_alone <- PRS2[, c('subjectkey','PRS_2')]

abcd.data.combined.harmonized <- merge(abcd.data.combined.harmonized,PRS1_alone,by="subjectkey")
abcd.data.combined.harmonized <- merge(abcd.data.combined.harmonized,PRS2_alone,by="subjectkey")
# 5815

```
# linear mixed effects models associating INT sub-fac with F1 separately
```{r}

summary(lmer(Factor4~PRS_1+interview_age+sex+(1|rel_family_id),data=abcd.data.combined.harmonized))
mod1<-lmer(Factor4~PRS_1+interview_age+sex+(1|rel_family_id),data=abcd.data.combined.harmonized)
tab_model(mod1,pred.labels = c("Intercept","PRS_1","Age","Sex"),dv.labels=c("INT"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste("Associations_F1_INT_COMBAT.doc", sep = ""))

confint(mod1)

```


# linear mixed effects models associating INT sub-fac with F2 separately including meanFD
```{r}

summary(lmer(Factor4~PRS_2+interview_age+sex+(1|rel_family_id),data=abcd.data.combined.harmonized))
mod1<-lmer(Factor4~PRS_2+interview_age+sex+(1|rel_family_id),data=abcd.data.combined.harmonized)
tab_model(mod1,pred.labels = c("Intercept","PRS_2","Age","Sex"),dv.labels=c("INT"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste("Associations_F2_INT_COMBAT.doc", sep = ""))

confint(mod1)
```

