---
title: "Associations_PFN_Psychopath"
author: "Arielle Keller/Kevin Sun"
date: "3/21/2022 update 11/30/22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width=250)
library(tidyr)
library(dplyr)
library(ggplot2)
library(lsr)
library(lme4)
library(lmerTest)
library(mediation)
library(ggcorrplot)
library(corrplot)
library(RColorBrewer)
library(glmnet)
library(mgcv)
library(gamm4)
library(readr)

library(devtools)
install_github("jfortin1/neuroCombatData")
install_github("jfortin1/neuroCombat_Rpackage")
library(neuroCombat)

library(R.matlab)
library(mgcv)
library(ggplot2)
library(visreg)
library(ggtext)
library(sjPlot)
library(Gmisc)
```

# Setup output folder
```{r}

dout <- "./Baseline_pfac_with_All_PFNs"
dir.create(dout)
sink(file=paste0(dout,"/This_output.txt"), split=TRUE)
```


# First load in the spatial extent of each PFN (they're in order, 1-17)
```{r}
pfn_sizes <- read.csv("../All_PFN_sizes.csv") # n=9,132
# Change PFN column names so they're sensible
colnames(pfn_sizes)<-c("subjectkey","PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17")
pfn_sizes$subjectkey<-gsub('sub-NDARINV','NDAR_INV',pfn_sizes$subjectkey)
```



# Remove subjects based on the following criteria:
## 1) 8min of retained TRs (600 TRs)
## 2) ABCD Booleans for rest and T1
```{r}
num_TRs <- read.csv("../num_TRs_by_subj_redo.csv")
data<-merge(pfn_sizes,num_TRs,by="subjectkey")
data.clean<-data[data$numTRs>=600,]

# Remove participants based on booleans from ABCD
abcd_imgincl01 <- read.csv("../abcd_imgincl01.csv")
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$eventnam=="baseline_year_1_arm_1",]
abcd_imgincl01 <- abcd_imgincl01[!abcd_imgincl01$visit=="",] 
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_t1w_include==1,]
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_rsfmri_include==1,] 

combined.data <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey") #7475
```



## Import the Psychopathology bifactor scores from DEAP
```{r}
newdata<-readRDS("DEAP-data-download_ABCD_psychopathology_bifactor_scores_BASELINE.rds")
newdata.baseline<-newdata[newdata$event_name=="baseline_year_1_arm_1",]
colnames(newdata.baseline)[1]<-"subjectkey"
all.data <- merge(combined.data,newdata.baseline[,c("subjectkey", setdiff(colnames(newdata.baseline),colnames(combined.data)))],by="subjectkey") #7474

```



# Add in Family and Site covariates
```{r}
family <-read.table("../acspsw03.txt",header=TRUE)
family.baseline<-family[family$eventname=="baseline_year_1_arm_1",]
abcd.data.almost <- merge(all.data,family.baseline[, c("subjectkey", setdiff(colnames(family.baseline),colnames(all.data)))],by="subjectkey")
site_info <- readRDS("../DEAP-siteID.rds")
site.baseline<-site_info[site_info$event_name=="baseline_year_1_arm_1",]
colnames(site.baseline)[1]<-"subjectkey"
abcd.data.almost2 <- merge(abcd.data.almost,site.baseline[,c("subjectkey", setdiff(colnames(site.baseline),colnames(abcd.data.almost)))],by="subjectkey") #7474
```


# Add mean FD
```{r}
meanFD <- read.csv("../meanFD_031822.csv")
colnames(meanFD)<-c("subjectkey","meanFD")
meanFD$subjectkey <- gsub(pattern="sub-NDAR",replacement="NDAR_", meanFD$subjectkey)
abcd.data <- merge(abcd.data.almost2,meanFD,by="subjectkey") #7461
```


# Load discovery/replication matched samples -- Changed: matched_group 1 & 2 (>0) -> combined group
```{r}
traintest<-read_tsv("../participants.tsv")
traintest.baseline<-traintest[traintest$session_id=="ses-baselineYear1Arm1",c("participant_id","matched_group")]
colnames(traintest.baseline)[1]<-c("subjectkey")
traintest.baseline$subjectkey <- gsub(pattern="sub-NDAR",replacement="NDAR_", traintest.baseline$subjectkey)
traintest.baseline<-traintest.baseline %>% distinct()
abcd.data.traintest <- merge(abcd.data,traintest.baseline,by="subjectkey")
abcd.data.traintest<-abcd.data.traintest[!duplicated(abcd.data.traintest$subjectkey),] # remove duplicated subject
abcd.data.combined <- abcd.data.traintest[abcd.data.traintest$matched_group>0,] #7459
write.csv(abcd.data.combined,'abcd.data.combined.csv')
```



# Apply ComBat harmonization across ABCD sites separately for combined set
```{r}
# prep to make sure there are no empty levels
abcd.data.combined$abcd_site<-droplevels(abcd.data.combined$abcd_site)

# harmonize combined set 
batch <- abcd.data.combined$abcd_site
abcd.data.combined.toharmonize <- abcd.data.combined[,c("PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17","General_p","meanFD")]
mod <- model.matrix(~abcd.data.combined$interview_age+abcd.data.combined$sex+abcd.data.combined$rel_family_id)
dat <- t(abcd.data.combined.toharmonize)
abcd.data.combat <- neuroCombat(dat=dat,mod=mod,batch=batch,eb=FALSE)
dat.harmonized<-data.frame(t(abcd.data.combat$dat.combat))
abcd.data.noPFNsCog <- subset(abcd.data.combined,select=-c(PFN1,PFN2,PFN3,PFN4,PFN5,PFN6,PFN7,PFN8,PFN9,PFN10,PFN11,PFN12,PFN13,PFN14,PFN15,PFN16,PFN17,General_p,meanFD))
abcd.data.combined.harmonized <- cbind(abcd.data.noPFNsCog,dat.harmonized) # Add the harmonized data back into the main dataframe (BE AWARE THAT NOT ALL DATA IS HARMONIZED)

```


# fix age variable to be continuous
```{r}
abcd.data.combined.harmonized$interview_age <- as.numeric(abcd.data.combined.harmonized$interview_age)
abcd.data.traintest$interview_age <- as.numeric(abcd.data.traintest$interview_age)
```


# standardize all variables for LMER
```{r}
abcd.data.combined.harmonized$PFN1<-(abcd.data.combined.harmonized$PFN1-mean(abcd.data.combined.harmonized$PFN1,na.rm=TRUE))/sd(abcd.data.combined.harmonized$PFN1,na.rm=TRUE)
abcd.data.combined.harmonized$PFN2<-(abcd.data.combined.harmonized$PFN2-mean(abcd.data.combined.harmonized$PFN2,na.rm=TRUE))/sd(abcd.data.combined.harmonized$PFN2,na.rm=TRUE)
abcd.data.combined.harmonized$PFN3<-(abcd.data.combined.harmonized$PFN3-mean(abcd.data.combined.harmonized$PFN3,na.rm=TRUE))/sd(abcd.data.combined.harmonized$PFN3,na.rm=TRUE)
abcd.data.combined.harmonized$PFN4<-(abcd.data.combined.harmonized$PFN4-mean(abcd.data.combined.harmonized$PFN4,na.rm=TRUE))/sd(abcd.data.combined.harmonized$PFN4,na.rm=TRUE)
abcd.data.combined.harmonized$PFN5<-(abcd.data.combined.harmonized$PFN5-mean(abcd.data.combined.harmonized$PFN5,na.rm=TRUE))/sd(abcd.data.combined.harmonized$PFN5,na.rm=TRUE)
abcd.data.combined.harmonized$PFN6<-(abcd.data.combined.harmonized$PFN6-mean(abcd.data.combined.harmonized$PFN6,na.rm=TRUE))/sd(abcd.data.combined.harmonized$PFN6,na.rm=TRUE)
abcd.data.combined.harmonized$PFN7<-(abcd.data.combined.harmonized$PFN7-mean(abcd.data.combined.harmonized$PFN7,na.rm=TRUE))/sd(abcd.data.combined.harmonized$PFN7,na.rm=TRUE)
abcd.data.combined.harmonized$PFN8<-(abcd.data.combined.harmonized$PFN8-mean(abcd.data.combined.harmonized$PFN8,na.rm=TRUE))/sd(abcd.data.combined.harmonized$PFN8,na.rm=TRUE)
abcd.data.combined.harmonized$PFN9<-(abcd.data.combined.harmonized$PFN9-mean(abcd.data.combined.harmonized$PFN9,na.rm=TRUE))/sd(abcd.data.combined.harmonized$PFN9,na.rm=TRUE)
abcd.data.combined.harmonized$PFN10<-(abcd.data.combined.harmonized$PFN10-mean(abcd.data.combined.harmonized$PFN10,na.rm=TRUE))/sd(abcd.data.combined.harmonized$PFN10,na.rm=TRUE)
abcd.data.combined.harmonized$PFN11<-(abcd.data.combined.harmonized$PFN11-mean(abcd.data.combined.harmonized$PFN11,na.rm=TRUE))/sd(abcd.data.combined.harmonized$PFN11,na.rm=TRUE)
abcd.data.combined.harmonized$PFN12<-(abcd.data.combined.harmonized$PFN12-mean(abcd.data.combined.harmonized$PFN12,na.rm=TRUE))/sd(abcd.data.combined.harmonized$PFN12,na.rm=TRUE)
abcd.data.combined.harmonized$PFN13<-(abcd.data.combined.harmonized$PFN13-mean(abcd.data.combined.harmonized$PFN13,na.rm=TRUE))/sd(abcd.data.combined.harmonized$PFN13,na.rm=TRUE)
abcd.data.combined.harmonized$PFN14<-(abcd.data.combined.harmonized$PFN14-mean(abcd.data.combined.harmonized$PFN14,na.rm=TRUE))/sd(abcd.data.combined.harmonized$PFN14,na.rm=TRUE)
abcd.data.combined.harmonized$PFN15<-(abcd.data.combined.harmonized$PFN15-mean(abcd.data.combined.harmonized$PFN15,na.rm=TRUE))/sd(abcd.data.combined.harmonized$PFN15,na.rm=TRUE)
abcd.data.combined.harmonized$PFN16<-(abcd.data.combined.harmonized$PFN16-mean(abcd.data.combined.harmonized$PFN16,na.rm=TRUE))/sd(abcd.data.combined.harmonized$PFN16,na.rm=TRUE)
abcd.data.combined.harmonized$PFN17<-(abcd.data.combined.harmonized$PFN17-mean(abcd.data.combined.harmonized$PFN17,na.rm=TRUE))/sd(abcd.data.combined.harmonized$PFN17,na.rm=TRUE)

abcd.data.combined.harmonized$interview_age<-(abcd.data.combined.harmonized$interview_age-mean(abcd.data.combined.harmonized$interview_age,na.rm=TRUE))/sd(abcd.data.combined.harmonized$interview_age,na.rm=TRUE)
abcd.data.combined.harmonized$meanFD<-(abcd.data.combined.harmonized$meanFD-mean(abcd.data.combined.harmonized$meanFD,na.rm=TRUE))/sd(abcd.data.combined.harmonized$meanFD,na.rm=TRUE)

```

# Make a demographics table
```{r}
# exclude subjects with missing cognitive data
abcd.data.for.ridge<-abcd.data.traintest[,c("subjectkey","General_p","matched_group","interview_age","sex","meanFD","abcd_site","rel_family_id")]

abcd.data.traintest<-abcd.data.traintest[complete.cases(abcd.data.for.ridge),]


library(Gmisc)
demo_table <- abcd.data.traintest %>%
  mutate(matched_group = factor(matched_group, levels = 1:2, labels = c("Discovery", "Replication"))) %>%
#subset(matched_group<3) %>%
  set_column_labels(interview_age = "Age (Months)",
                    sex = "Sex",
                    race.6level = "Race",
                    household.income = "Household Income",
                    General_p = "P-factor",
                    high.educ = "Parent Education") %>%
  getDescriptionStatsBy(interview_age, 
                        sex,
                        General_p,
                        household.income,
                        race.6level,
                        high.educ,
                        add_total_col = TRUE, statistics=TRUE,
                        by = matched_group)

demo_table

```

# ********************************************************************
# *   Process General_p                                              *
# ********************************************************************


# linear mixed effects models associating Gen P with each PFN
```{r}

cat("\n********************************************************************\n")
cat("*   Process General_p                                              *\n")
cat("********************************************************************\n\n")

cat("\n> summary(lmer(PFN1~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
summary(lmer(PFN1~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> summary(lmer(PFN2~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
summary(lmer(PFN2~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> summary(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
summary(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> summary(lmer(PFN4~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
summary(lmer(PFN4~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> summary(lmer(PFN5~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
summary(lmer(PFN5~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> summary(lmer(PFN6~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
summary(lmer(PFN6~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> summary(lmer(PFN7~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
summary(lmer(PFN7~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> summary(lmer(PFN8~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
summary(lmer(PFN8~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> summary(lmer(PFN9~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
summary(lmer(PFN9~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> summary(lmer(PFN10~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
summary(lmer(PFN10~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> summary(lmer(PFN11~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
summary(lmer(PFN11~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> summary(lmer(PFN12~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
summary(lmer(PFN12~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> summary(lmer(PFN13~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
summary(lmer(PFN13~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> summary(lmer(PFN14~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
summary(lmer(PFN14~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> summary(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
summary(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> summary(lmer(PFN16~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
summary(lmer(PFN16~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> summary(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
summary(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))


mod1<-lmer(PFN1~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)
mod2<-lmer(PFN2~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)
mod3<-lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)
mod4<-lmer(PFN4~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)
mod5<-lmer(PFN5~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)
mod6<-lmer(PFN6~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)
mod7<-lmer(PFN7~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)
mod8<-lmer(PFN8~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)
mod9<-lmer(PFN9~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)
mod10<-lmer(PFN10~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)
mod11<-lmer(PFN11~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)
mod12<-lmer(PFN12~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)
mod13<-lmer(PFN13~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)
mod14<-lmer(PFN14~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)
mod15<-lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)
mod16<-lmer(PFN16~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)
mod17<-lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)

tab_model(mod1,mod2,mod3,pred.labels = c("Intercept","Age","Sex","Mean FD","General_p"),dv.labels=c("PFN1","PFN2","PFN3"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste0(dout,"/Associations_PFN123_General_p.doc"))

tab_model(mod4,mod5,mod6,pred.labels = c("Intercept","Age","Sex","Mean FD","General_p"),dv.labels=c("PFN4","PFN5","PFN6"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste0(dout,"/Associations_PFN456_General_p.doc"))

tab_model(mod7,mod8,mod9,pred.labels = c("Intercept","Age","Sex","Mean FD","General_p"),dv.labels=c("PFN7","PFN8","PFN9"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste0(dout,"/Associations_PFN789_General_p.doc"))

tab_model(mod10,mod11,mod12,pred.labels = c("Intercept","Age","Sex","Mean FD","General_p"),dv.labels=c("PFN10","PFN11","PFN12"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste0(dout,"/Associations_PFN101112_General_p.doc"))

tab_model(mod13,mod14,mod15,pred.labels = c("Intercept","Age","Sex","Mean FD","General_p"),dv.labels=c("PFN13","PFN14","PFN15"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste0(dout,"/Associations_PFN131415_General_p.doc"))

tab_model(mod16,mod17,pred.labels = c("Intercept","Age","Sex","Mean FD","General_p"),dv.labels=c("PFN16","PFN17"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste0(dout,"/Associations_PFN1617_General_p.doc"))

```

# get confidence intervals
```{r}
cat("\n---- get confidence intervals ----\n")

cat("\n> confint(lmer(PFN1~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
confint(lmer(PFN1~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> confint(lmer(PFN2~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
confint(lmer(PFN2~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> confint(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
confint(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> confint(lmer(PFN4~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
confint(lmer(PFN4~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> confint(lmer(PFN5~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
confint(lmer(PFN5~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> confint(lmer(PFN6~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
confint(lmer(PFN6~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> confint(lmer(PFN7~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
confint(lmer(PFN7~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> confint(lmer(PFN8~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
confint(lmer(PFN8~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> confint(lmer(PFN9~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
confint(lmer(PFN9~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> confint(lmer(PFN10~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
confint(lmer(PFN10~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> confint(lmer(PFN11~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
confint(lmer(PFN11~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> confint(lmer(PFN12~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
confint(lmer(PFN12~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> confint(lmer(PFN13~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
confint(lmer(PFN13~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> confint(lmer(PFN14~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
confint(lmer(PFN14~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> confint(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
confint(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> confint(lmer(PFN16~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
confint(lmer(PFN16~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
cat("\n> confint(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)):\n")
confint(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))

```


### Bar plot (Combined Sample):
```{r}
pfn1<-summary(lmer(PFN1~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
pfn2<-summary(lmer(PFN2~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
pfn3<-summary(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)) 
pfn4<-summary(lmer(PFN4~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
pfn5<-summary(lmer(PFN5~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)) 
pfn6<-summary(lmer(PFN6~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
pfn7<-summary(lmer(PFN7~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized)) 
pfn8<-summary(lmer(PFN8~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
pfn9<-summary(lmer(PFN9~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
pfn10<-summary(lmer(PFN10~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
pfn11<-summary(lmer(PFN11~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
pfn12<-summary(lmer(PFN12~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
pfn13<-summary(lmer(PFN13~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
pfn14<-summary(lmer(PFN14~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
pfn15<-summary(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
pfn16<-summary(lmer(PFN16~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))
pfn17<-summary(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+General_p,data=abcd.data.combined.harmonized))

p_vec<-c(pfn1$coefficients[5,5],pfn2$coefficients[5,5],pfn3$coefficients[5,5],pfn4$coefficients[5,5],pfn5$coefficients[5,5],pfn6$coefficients[5,5],pfn7$coefficients[5,5],pfn8$coefficients[5,5],pfn9$coefficients[5,5],pfn10$coefficients[5,5],pfn11$coefficients[5,5],pfn12$coefficients[5,5],pfn13$coefficients[5,5],pfn14$coefficients[5,5],pfn15$coefficients[5,5],pfn16$coefficients[5,5],pfn17$coefficients[5,5])

p_vec_adj <- p.adjust(p_vec, "fdr") #fdr correction
print(p_vec_adj)
z_vec <- qnorm(p_vec/2,lower.tail = FALSE);

pos_neg<-c(pfn1$coefficients[5,1],pfn2$coefficients[5,1],pfn3$coefficients[5,1],pfn4$coefficients[5,1],pfn5$coefficients[5,1],pfn6$coefficients[5,1],pfn7$coefficients[5,1],pfn8$coefficients[5,1],pfn9$coefficients[5,1],pfn10$coefficients[5,1],pfn11$coefficients[5,1],pfn12$coefficients[5,1],pfn13$coefficients[5,1],pfn14$coefficients[5,1],pfn15$coefficients[5,1],pfn16$coefficients[5,1],pfn17$coefficients[5,1])
pos_neg <- ifelse(pos_neg>0,1,-1)

z_vec_pn_combined <- z_vec*pos_neg
keep_p <- ifelse(p_vec_adj<.05,1,0)
print(keep_p)

z_vec_sorted = rank(z_vec_pn_combined);
pfn_inAscend <- c()
for (t in c(1:17)) { pfn_inAscend <- append(pfn_inAscend,which(z_vec_sorted == t))}

# Using 7 colors scheme for bar plot
# bar plot for Psychopath effects
data <- data.frame(PsychopathEffects_Z = as.numeric(z_vec_pn_combined)) 
data$EffectRank <- as.numeric(z_vec_sorted)
# BorderColor1 is for colors of 1-17 network numbers(to lable the network numbers in a 1-17 order)
BorderColor1 <- c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E", 
                 "#4E31A8", "#F5BA2E");
				 
# BorderColor2 is for colors of bar fill 1-17 networks (in a 1-17 order). If the bar is nofill, change the code to "#FFFFFF" for that PFN. ("black" is filled with black)
BorderColor2 <- c("#FFFFFF", "#FFFFFF", "#FFFFFF", "#7499C2", "#FFFFFF",
                 "#FFFFFF", "#FFFFFF", "#FFFFFF", "#E443FF", "#FFFFFF",
                 "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#F5BA2E", 
                 "#4E31A8", "#FFFFFF");
# Change the color order
BorderColor <- BorderColor1[pfn_inAscend]
BorderColor3 <- BorderColor2[pfn_inAscend]

# the line type for the 1-17 network bars (in a 1-17 order).  If a dashed line is needed for a bar, please change the value to "dashed".
LineType <- c("dashed", "dashed", "dashed", "solid", "dashed",
              "dashed", "dashed", "dashed", "solid", "dashed",
              "dashed", "dashed", "dashed", "dashed", "solid",
              "solid", "dashed");

Fig <- ggplot(data, aes(EffectRank, PsychopathEffects_Z)) +
  geom_bar(stat = "identity", fill=BorderColor3[z_vec_sorted], 
           colour = BorderColor[z_vec_sorted], linetype = LineType, width = 0.8) + 
  labs(x = "Networks", y = paste0("General_p", " Association (Z)")) + theme_classic() +
  theme(axis.text.x = ggtext::element_markdown(size= 27, color = BorderColor), 
        axis.text.y = ggtext::element_markdown(size= 33, color = "black"), 
        axis.title=ggtext::element_markdown(size = 33)) +
  theme(axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1)) +
  scale_x_discrete(labels = as.character(pfn_inAscend),limits = as.character(z_vec_sorted)) 
Fig
ggsave(paste0(dout,"/NetworkSize_Loading_General_p_FDR.tiff"), width = 19, height = 16, dpi = 600, units = "cm");



```





